\EVOSUITE at the SBST 2017 Tool Competition

### 2017-02-22 papers/sbst17/paper_sbst17.tex
drop todo

This year, the contest also included manually written test suites as
baseline (only for 63 out of the 69 benchmarks). The results indicate
that there is no significant difference in branch coverage between
\EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
written ones (avg. \AvgCovManual), with Vargha-Delaney's
$A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
scores, however, the results show
that---unsurprisingly---automatically generated assertions are weaker
than manually written ones: the average \EVOSUITE mutation score for
these 63 benchmarks is \AvgMutEvosuite, significantly lower than the
average \AvgMutManual obtained by developer-written test suites, with
$A_{12}=\EvoManMutA$ and $p\EvoManMutPV$.\TODO{Does showing A12 make
  sense if there's only one manual test suite per benchmark?}

>>>>

This year, the contest also included manually written test suites as
baseline (only for 63 out of the 69 benchmarks). The results indicate
that there is no significant difference in branch coverage between
\EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
written ones (avg. \AvgCovManual), with Vargha-Delaney's
$A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
scores, however, the results show
that---unsurprisingly---automatically generated assertions are weaker
than manually written ones: the average \EVOSUITE mutation score for
these 63 benchmarks is \AvgMutEvosuite, significantly lower than the
average \AvgMutManual obtained by developer-written test suites, with
$A_{12}=\EvoManMutA$ and $p\EvoManMutPV$.
